Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-03-20 article.rnw
Explain in the methods the statistics and tests calculated from the Akaike weights.
That is, all the calculations performed before creating the coclassification matrices.

>>>>

From the Akaike weights, we calculated two important statistics.
Firstly, the total Akaike weight of models with a lower AIC than the entirely ungrouped model; this is the probability that some model is more parsimonious than the ungrouped model.
Secondly, the total Akaike weight of models that used the same grouping for the rows as for the columns; this is the probability that the most parsimonious model grouped species equivalently in their competitive effects as in their competitive responses.
To evaluate the significance of the latter, we performed a Monte Carlo permutation test, comparing the total Akaike weight of those models that grouped rows and columns equivalently to the total Akaike weight of a random equally-sized subset of the models.
%This is a test of whether the most parsimonious model is more likely to group the species equivalently in the rows as in the columns than it would be by chance.
%TODO: Is this test superseded by the Mantel test of row vs column coclassification?
%TODO: Should this test simply be a t-test on the raw AIC values? I think not, as we're interested in the best, rather than the mean.
